---
output:
  pdf_document: default
  html_document: default
---
```{r, echo=FALSE, warning=FALSE, include=FALSE}
library(DT)
library(data.table)
source("R/simulation_functions.R")

knitr::opts_chunk$set(echo = F)

```

# MSN Simulation

## Topic: Migraine

Using a set of defined medic attributes ([see here](https://docs.google.com/spreadsheets/d/1-l8WyTSV7JMddlptHg4S4xnAgNFXwsYtbn_NTGj9gXc/edit#gid=1728361188)), we want to find out how many specialists at least have one of these attributes. For this, we simulate patients at different locations and different travel distances (CAVE: here, air distance). 

For every location, we detect the matching medics either working in a practice or in a clinic within a distance of 5, 10, 50, 100 km. We first show a summary for every location and then provide detailed medic's activities information per simulation configuration (CAVE: # activities > # medics).

```{r, echo=FALSE, include=FALSE}
# Köln
lat = 50.93785139297979
lng = 6.9551170454236795

sim_result = run_location_simulation(lng=lng, lat=lat)
```

### Location: Köln

#### Summary

```{r, echo=F}
DT::datatable(sim_result[["summary"]])
```

#### Workplace: Practice

##### Practice - 5 km radius

```{r}
DT::datatable(sim_result[["medics"]][["practice"]][[5]])
```

##### Practice - 10 km radius

```{r}
DT::datatable(sim_result[["medics"]][["practice"]][[10]])
```

##### Practice - 50 km radius

```{r}
DT::datatable(sim_result[["medics"]][["practice"]][[50]])
```

##### Practice - 100 km radius

```{r}
DT::datatable(sim_result[["medics"]][["practice"]][[100]])
```

#### Workplace: Clinic

##### Clinic - 5 km radius

```{r}
DT::datatable(sim_result[["medics"]][["clinic"]][[5]])
```

##### Clinic - 10 km radius

```{r}
DT::datatable(sim_result[["medics"]][["clinic"]][[10]])
```

##### Clinic - 50 km radius

```{r}
DT::datatable(sim_result[["medics"]][["clinic"]][[50]])
```

##### Clinic - 100 km radius

```{r}
DT::datatable(sim_result[["medics"]][["clinic"]][[100]])
```


```{r, echo=FALSE, include=FALSE}
# Sonneberg, Thüringen
lat = 50.35662196480167
lng = 11.170345578752212

sim_result = run_location_simulation(lng=lng, lat=lat)
```

### Location: Sonneberg, Thüringen

#### Summary

```{r, echo=F}
DT::datatable(sim_result[["summary"]])
```

#### Workplace: Practice

##### Practice - 5 km radius

```{r}
DT::datatable(sim_result[["medics"]][["practice"]][[5]])
```

##### Practice - 10 km radius

```{r}
DT::datatable(sim_result[["medics"]][["practice"]][[10]])
```

##### Practice - 50 km radius

```{r}
DT::datatable(sim_result[["medics"]][["practice"]][[50]])
```

##### Practice - 100 km radius

```{r}
DT::datatable(sim_result[["medics"]][["practice"]][[100]])
```

#### Workplace: Clinic

##### Clinic - 5 km radius

```{r}
DT::datatable(sim_result[["medics"]][["clinic"]][[5]])
```

##### Clinic - 10 km radius

```{r}
DT::datatable(sim_result[["medics"]][["clinic"]][[10]])
```

##### Clinic - 50 km radius

```{r}
DT::datatable(sim_result[["medics"]][["clinic"]][[50]])
```

##### Clinic - 100 km radius

```{r}
DT::datatable(sim_result[["medics"]][["clinic"]][[100]])
```
